EDIpack: A generic and interoperable Lanczos-based solver for quantum impurity problems

### 2025-05-22 05_examples.tex

In the anti-adiabatic limit, the Holstein interaction takes a
particularly simple form:
\begin{equation}\label{HlikeAttraction}
    H_\mathrm{int} \overset{ \omega_0 \rightarrow \infty}{ \longrightarrow } -\frac{\lambda}{2} \sum_i \Big[\sum_\sigma(c^\dagger_{i\sigma}c_{i\sigma} -\frac{1}{2}) \Big]^2
\end{equation}
which describes a local Hubbard-like attraction among electrons
(mediated by local phonons).
In the opposite, adiabatic, limit, $\omega_0 \rightarrow 0$ the system
enters in a Bipolaronic Insulating phase~\citep{Capone2006PRB} for our
choice of the coupling.

>>>>

In the anti-adiabatic limit, the Holstein interaction takes a
particularly simple form:
\begin{equation}\label{HlikeAttraction}
    H_\mathrm{int} \overset{ \omega_0 \rightarrow \infty}{ \longrightarrow } -\frac{\lambda}{2} \sum_i \Big[\sum_\sigma(c^\dagger_{i\sigma}c_{i\sigma} -\frac{1}{2}) \Big]^2
\end{equation}
which describes a local Hubbard-like attraction among electrons
(mediated by local phonons).
In the opposite, adiabatic, limit, $\omega_0 \rightarrow 0$ the system
enters in a Bipolaronic Insulating phase~\cite{Capone2006PRB} for our
choice of the coupling.
